Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-06-24 numerical-mhd-dedner.tex
edited dedner MHD section

The method is dimensionally un-split in that the fluxes are computed
for all dimensions first and the conserved quantities are updated in
one step, in contrast to the Strang splitting employed in the other solvers.
Also unlike the other schemes, time-integration is done with a second-order
Runge-Kutta scheme \citep{1988JCoPh..77..439S}.

Finally, we note that for cosmological simulations, this solver uses a slightly different definition of the magnetic field than used in the rest of the paper.  In particular, the field is defined as $\vecB = a^{3/2} \vecB^{\prime}$ (where $\vecB^{\prime}$ is the proper field strength).  This adds a source term of $-\dot{a}/(2a) \vecB$ on the right-hand side of equation~\ref{eq:induction}, removes the factor of $a$ in the $\vecB$ term in the energy equation (eq.~\ref{eq:total_energy_def}) and in the definition of the isotropic pressure $p^*$.

>>>>

The method is dimensionally un-split in that the fluxes are computed
for all dimensions first and the conserved quantities are updated in
one step, in contrast to the Strang splitting employed in the other
fluid methods described in this paper.
Also unlike the other schemes, time-integration is done with a second-order
Runge-Kutta scheme \citep{1988JCoPh..77..439S}.

Finally, we note that for cosmological simulations, this solver uses a
slightly different definition of the magnetic field than used in the
rest of the paper.  In particular, the field is defined as $\vecB =
a^{3/2} \vecB^{\prime}$ (where $\vecB^{\prime}$ is the proper field
strength).  This adds a source term of $-\dot{a}/(2a) \vecB$ on the
right-hand side of Equation~\ref{eq:induction} and removes the factor
of $a$ in the $\vecB$ term in the energy equation
(Eq.~\ref{eq:total_energy_def}) and in the definition of the isotropic
pressure $p^*$.
